Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-08 manuscript.tex
Update on Overleaf.

\cite{gasser_1939} experimentally confirmed with homogeneously selected neurons that the axonal delay is positively proportional to the axon diameter, i.e. the amount of myelin wrapped around the axon. Indeed, the oligodendrocytes, one of the many glial cells present in the Vertebrates' nervous system, produce  \cite{???}

@@

facilitates both the neural circuit function and the behavioural performance~\cite{fields_2015}. Experiments on mammals show that myelination is directly related to learning and memory consolidation, especially motor training and in enriched environments, and both at an early age and in older animals, due to its involvement in coupling the activity of distant neuron populations. It is worth highlighting that myelination becomes increasingly important in larger brains where conductance delays are substantial and brainwave rhythms are critical; synchrony errors can lead to neuropsychiatric and neurological dysfunctions. Some further studies show that oligodendrocytes may detect neuronal activity thanks to growth factors or neurotransmitters released through ion channels or via exocytosis.

>>>>

\cite{gasser_1939} experimentally confirmed with homogeneously selected neurons that the axonal delay is positively proportional to the axon diameter, i.e. the amount of myelin wrapped around the axon. Indeed, the oligodendrocytes, one of the many glial cells present in the Vertebrates' nervous system, produce  \citep{reynolds_1928}

@@

facilitates both the neural circuit function and the behavioural performance~\cite{fields_2015}. Experiments on mammals show that myelination is directly related to learning and memory consolidation, especially motor training and in enriched environments. This biological phenomenom both at an early age, where the amount of oligodendrocites is the particularly high in the central nervous system~\citep{reynolds_1928}, and in older animals, due to its involvement in coupling the activity of distant neuron populations. It is worth highlighting that myelination becomes increasingly important in larger brains where conductance delays are substantial and brainwave rhythms are critical; synchrony errors can lead to neuropsychiatric and neurological dysfunctions. Some further studies show that oligodendrocytes may detect neuronal activity thanks to growth factors or neurotransmitters released through ion channels or via exocytosis.
